{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-24 paper.tex
Cleaned up section to be rewritten by LAAS

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
    \caption{A user manipulating objects on top of an RFID mat (providing object
    localisation) with a NAO robot, while an operator monitors
    the interaction on a tablet that displays an {\tt uwds view} client [photo blurred for blind review].}

    \label{fig|l2torexample}
\end{figure}

%\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
\uwds has been used within the [hidden for blind review] project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with. In one of the scenarios of this
project, participants are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands to place the elephant
\textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside}
the house.  To assess the performance, the robot and the operator need to
compute spatial relationships between objects from the visual perspective of the
participant.

\subsection{Architecture}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    %\caption{Schema of the \uwds architecture used in the L2TOR project. }
    \caption{Schema of the \uwds architecture used in the [hidden for blind review] project. }
    \label{fig|l2torarchitecture}
\end{figure}

The interaction scenario requires a number of \uwds clients. The clients are
distributed across two computers (the robot and a Microsoft Windows-operated
tablet) that communicate with each other in order to synchronise the world
representations. Figure~\ref{fig|l2torarchitecture} illustrates the topology of
the \uwds network, that consists in the following clients:

\begin{itemize}
    \item \textbf{Kinect Head Tracker}: captures the location and the direction
        of the user's head -- maintains the {\tt human} \emph{Perspective} node;

    \item \textbf{Object RFID tracker}: updates the locations of the virtual
        objects based on RFID data;

    \item \textbf{NAO joint state publisher}: virtual representation of the
        robot -- maintains the {\tt robot} \emph{Perspective} node;

    \item \textbf{Visibility computation}: computes visibility based on
        \emph{Perspective} nodes;

    \item \textbf{Spatial relations computation}: extracts symbolic spatial relations
        between the virtual objects;

    \item \textbf{Game/Rules computation}: interaction manager based on \uwds
        clients' input.

\end{itemize}

%The L2TOR project features an additional scenario where the user performs the
The [hidden for blind review] project features an additional scenario where the user performs the
manipulations on a tablet computer instead of using physical objects. To
accommodate this change, we replaced the object detection \uwds client with a 3D
virtual object detection while the rest of the system remains the same.

Finally, we are evaluating the use of a hybrid platform that utilises both virtual and
physical objects at the same time.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
    \caption{TODO LAAS: update photo -> MuMMER picture?}
    \label{fig|mummer-example}
\end{figure}

%\uwds has been used within the European MuMMER project
\uwds has been used within the [hidden for blind review] project
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with.

TODO LAAS

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{l2tor}
    %\caption{Schema of the \uwds architecture used in the MuMMER project. }
    \caption{TODO LAAS update archi -- Schema of the \uwds architecture used in the [hidden for blind review] project. }
    \label{fig|mummerarchitecture}
\end{figure}

The interaction scenario requires a number of \uwds clients. The clients are
distributed across...

Figure~\ref{fig|mummerarchitecture} illustrates the topology of
the \uwds network...

TODO LAAS
